Stellar Bars in Isolated Gas-Rich Galaxies Do Not Slow Down

### 2022-04-04 paper/ms.tex
Cleanup

\author{Angus Beane$^{1*}$, Lars Hernquist$^1$, Elena D'Onghia$^2$, et al.}

@@

\item Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721, USA

\item Lol

@@

% \begin{figure*}
% \includegraphics[width=0.5\textwidth]{fig1a.pdf}
% \includegraphics[width=0.5\textwidth]{fig1b.pdf}
% \vspace{-4mm}
% \caption{\textbf{Distribution of stars in the Galactic halo.}  All-sky
%   Mollweide projection maps of the density of stars at 60 kpc
%   $<R_{\rm gal}<100$ kpc, smoothed by a Gaussian kernel with
%   FWHM$ =30^\circ$.  {\bf Left panel:} data based on K giant stars.
%   {\bf Right panel:} simulation that includes the dynamical response
%   of the halo to the orbit of the LMC.  Regions near the Galactic
%   mid-plane ($|b|<10^\circ$) and the LMC and SMC, as well as regions
%   of high extinction are masked in grey, while the positions of the
%   LMC and SMC are marked as white stars.  One arm of the Sagittarius
%   stream has been masked in sky coordinates, as indicated by the grey
%   region at $b>0^\circ$ and $-180^\circ<l<-150^\circ$.  The
%   overdensity in the south-west is the local wake caused by the
%   passage of the LMC.  The overdensity in the North is the collective
%   response of the Galaxy due to the arrival of the LMC.  Notice that
%   the dynamic range of the density contrast for the simulated map is
%   smaller than the observed map.}
% \vspace{-4mm}
% \end{figure*}

% \begin{figure}[t!]
%   \center
%   \includegraphics[width=0.48\textwidth]{fig2.pdf}
%   \caption{\textbf{Quantitative comparison between data and models.}
%     Mean density contrasts in regions encompassing the local wake
%     ($-60^\circ<b<-20^\circ$, $45^\circ<l<90^\circ$) and the
%     collective response ($30^\circ<b<60^\circ$,
%     $240^\circ<l<300^\circ$) are shown along the $x$ and $y$ axes.
%     There are four simulations spanning a range in LMC masses from
%     $0.8-2.5\times10^{11}M_\odot$ (small-to-large green circles).  The
%     smooth model\cite{Rybizki18} is close to zero along both axes as
%     expected.  The dotted lines indicate uniform distributions (no
%     density contrast) on the x and y axes.  The density enhancement of
%     the local wake is measured at a significance of $5\sigma$ (error
%     bars on the data represent $1\sigma$ Poisson uncertainties) and
%     the mean density is $1.4\pm0.2$ times larger in the data than in
%     the fiducial simulation.}
% \end{figure}

@@

%\bibliographystyle{naturemag}
\bibliography{ref}

@@

\item [Acknowledgements] We thank both referees for their constructive
  feedback.  C.C. is partially supported by the Packard
  Foundation.  R.P.N. gratefully acknowledges an Ashford Fellowship
  and Peirce Fellowship granted by Harvard University.  G.B.  and
  N.G.-C. are supported by HST grant AR 15004, NASA ATP grant
  17-ATP17-0006, NSF CAREER AST-1941096.  A.B. acknowledges support
  from NASA through HST grant HST-GO-15930.  All the simulations were
  run on El-Gato super computer which was supported by the National
  Science Foundation under Grant No. 1228509.  We have made use of
  data from the European Space Agency mission Gaia
  (http://www.cosmos.esa.int/gaia), processed by the Gaia Data
  Processing and Analysis Consortium (DPAC; see
  http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for
  DPAC has been provided by national institutions, in particular the
  institutions participating in the Gaia Multilateral Agreement.  This
  publication makes use of data products from the {\it Wide-field
    Infrared Survey Explorer}, which is a joint project of the
  University of California, Los Angeles, and the Jet Propulsion
  Laboratory/California Institute of Technology, and NEOWISE, which is
  a project of the Jet Propulsion Laboratory/ California Institute of
  Technology.  {\it WISE} and NEOWISE are funded by the National
  Aeronautics and Space Administration.

\item[Author Contributions] C.C. and R.P.N. jointly conceived of the
  project.  C.C. led the analysis of the data.  N.G-C. and
  G.B. provided the simulation data and aided in its interpretation.
  All authors contributed to aspects of the analysis and to the
  writing of the manuscript.

\item[Author  Information]  Reprints and permissions
    information is available at npg.nature.com/reprintsandpermissions.
    Correspondence and requests for materials should be addressed to
    C.C.\ (cconroy@cfa.harvard.edu).

  \item[Data Availability] The K giant catalog used in this paper is
    available at \texttt{https://doi.org/10.7910/DVN/2D1H8J}.

  \item[Code Availability] We have opted not to make the code used in
    this manuscript available because the data reduction and analysis
    is straightforward and can be easily reproduced following the
    methods described herein.

@@

% \begin{figure}[t!]
%   \includegraphics[width=0.45\textwidth]{ed_fig1.pdf}
%   \vspace{-1cm}
%   \caption{\textbf{Extended Data Figure 1 $|$ Photometric selection of
%       giants.}  Color-color diagram for stars at high Galactic
%     latitude ($b>45^\circ$) with {\it Gaia} parallax $\pi<0.1$ mas.
%     Two sequences are clearly visible, with the upper branch being
%     associated with giant stars, and the lower with dwarf stars. The
%     red lines mark the selection boundary used in this work.}
% \end{figure}

% \begin{figure}[t!]
%   \includegraphics[width=0.45\textwidth]{ed_fig2.pdf}
%   \caption{\textbf{Extended Data Figure 2 $|$ Test of Photometric
%       Distances.}  Comparison of our photometric distances against
%     literature values for satellite galaxies around the Milky Way
%     (red) and globular clusters (blue).  Error bars represent the
%     $1\sigma$ scatter in the photometric distances and dotted lines
%     mark $\pm20$\% about the one-to-one line.  The dwarf galaxies
%     include Fornax, Draco, Sculptor, Carina, Ursa Minor, and the LMC
%     and SMC, and span average metallicities from [Fe/H]$\approx-0.5$
%     (LMC) to $-2.2$ (Ursa Minor)\cite{McConnachie12}.}
% \end{figure}

% \begin{figure*}[t!]
%   \includegraphics[width=0.5\textwidth]{ed_fig3a.pdf}
%   \includegraphics[width=0.5\textwidth]{ed_fig3b.pdf}
%   \caption{\textbf{Extended Data Figure 3 $|$ Maps of un-smoothed star
%       counts.}  Mollweide projection maps of the observed sample of
%     giants with pixels of size 13.4 sq. deg. {\bf Left panel:} map
%     with no masking of known structure, either in sky coordinates or
%     proper motions.  The two main features identified here, the
%     transient wake and the collective response, are still clearly
%     visible even in this unfiltered map.  The LMC and SMC appear in
%     the lower right as a merged region of high density.  Other
%     features include the stellar disk+bulge in the center, and the
%     Sagittarius stream both in the north-center and lower left and
%     right.  {\bf Right panel:} map showing the filtered catalog used
%     in Fig 1a.}
% \end{figure*}

% \begin{figure*}[t!]
%   \center
%   \includegraphics[width=0.8\textwidth]{ed_fig4.pdf}
%   \caption{ \textbf{Extended Data Figure 4 $|$ Proper motions of the
%       halo sample.}  {\bf a:} proper motions of the K giants at
%     $60<R_{\rm gal}<100$ kpc with $12<W1<15$ and the LMC and SMC
%     removed via on-sky selection.  {\bf b:} solar reflex-corrected
%     proper motions.  Notice the much tighter distribution of stars
%     near (0,0).  In this panel the Sagittarius dSph is visible at
%     (-2.5,-0.7), LMC and SMC stars not removed by the on-sky selection
%     are visible as a narrow vertical vertical strip at
%     $\mu_\alpha\gtrsim0.5$ mas yr$^{-1}$.  The Northern Sagittarius
%     arm is the large overdensity at (-0.7,0.0), and a Southern arm of
%     Sagittarius is the diagonal cluster of points at $\mu_\delta<-0.5$
%     mas yr$^{-1}$.  {\bf c:} reflex-corrected proper motions focusing
%     on the region of the sky containing the Northern Sagittarius arm
%     at $l\sim0^\circ$.  The red box indicates our selection for
%     removing this feature.  {\bf d:} stars not in the selection shown
%     in panel {\bf c}. Our selection for low proper motion stars is
%     indicated by a blue circle in {\bf c, d}.}
% \end{figure*}

>>>>

\author{Angus Beane$^{1*}$, Lars Hernquist$^1$, Elena D'Onghia$^{2,3}$, et al.}

@@

\item Department of Physics, University of Wisconsin-Madison, Madison, WI, USA

\item Department of Astronomy, University of Wisconsin-Madison, Madison, WI, USA

@@

@@

\bibliography{ref}

@@

\item [Acknowledgements] Foo.

\item[Author Contributions] Foo.

  \item[Data Availability] Foo.

  \item[Code Availability] Foo.

@@
